Abstract

### 2025-01-23 output/Letter_to_editor_reviewers.Rmd
Version responses to Reviewer 2 (WiP)

@@

Our manuscript presents a generalization of the multidimensional IRT parameters
introduced by Reckase and Reckase & McKinley in their articles
["The difficulty of test items that measure more than one ability" (1985)][1]
and
["The discriminating power of items that measure more than one dimension"
(1991)][2],
respectively.

[1]: https://doi.org/10.1177/014662168500900409

[2]: https://doi.org/10.1177/014662169101500407

@@

@@

@@

@@

>>>>

```{r setup}
#| include: false

# Includes:

library(here)
library(knitr)
library(patchwork)
library(ggplot2)
library(rstudioapi)
library(svglite) # Used by {knitr} and {ggplot2} to render the figure to SVG;
                 #   added to prevent {renv} from reporting inconsistent state.
library(officer)

ROOT_DIR <- here()
DOC_DIR  <- file.path(ROOT_DIR, "output")

opts_knit$set(root.dir = ROOT_DIR)
opts_chunk$set(
  echo     = FALSE,
  message  = FALSE,
  cache    = FALSE,
  dev      = "png",
  dpi      = 1200L,
  dev.args = list(type = "cairo-png"),
  tab.cap.fp_text = fp_text_lite(italic = FALSE, bold = TRUE),
  fig.cap.fp_text = fp_text_lite(italic = FALSE, bold = TRUE)
)

# Output configuration options:
options(digits = 3)
```

```{r write-bib}
# automatically create a bib database for R packages
write_bib(
  c(.packages(), 'bookdown', 'knitr', 'rmarkdown'),
  'www/packages.bib'
)
```

```{r sources}
#| cache:   false
#| include: false
source("R/Formulae.R",  encoding = 'UTF-8')
source("R/Constants.R", encoding = 'UTF-8')
```

@@

@@

Although the graphical representation is limited to two dimensions, we propose a general algebraic formulation that may account for any number of dimensions.
we have found our previous version to not be explicit enough about this, so we have updated the first paragraph of the "Model Formulation" section to read as follows:

    > Consider a basis $`r LS_BASIS_EQ`$,
    with $`r LS_BASIS`$ generally non-orthonormal.
    Let $`r LATENT_SPACE`$ be a $`r N_DIMS`$-dimensional latent space
    in basis $`r LS_BASIS`$ (with $`r N_DIMS`$ any positive integer),
    where a respondent is represented by vector $`r TRAIT_VEC_IN_LS`$.
    According to the `r MODEL_ACRONYM` model, the probability of
    a positive response to item $`r ITEM_INDEX`$ is [...]

@@

Thank you so much to Reviewer 2 for pointing out this typo.
We have corrected it in the manuscript accordingly.

@@

This case was also a typo; we have now corrected it in the manuscript as well.

@@

Our intention in Equations (26) and (27) was to express the item vector coordinates in terms of the original model parameters directly.
To do that, we have made use of the expression $`r DISCR_VECTOR_COORDS_EQ`$, stated in p. 7.
(That is, the geometric coordinates in the original test-space basis are equal to the algebraic values of the discrimination parameter.)
However, we acknowledge that we have skipped a step in our discrourse, thus making harder than necessary to follow along.
To correct this, we have modified the immediately preceding paragraph to the following:

    > Of course,
    from Equations \@ref(eq:origin-coords-result) and \@ref(eq:end-coords-result)
    it is easy to express the coordinates in terms of the parameters in the original
    model formulation.
    Given $`r DISCR_VECTOR_COORDS_EQ`$, we can express the coordinates as

### 2025-01-23 output/Main_text.Rmd
Version responses to Reviewer 2 (WiP)

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$
in basis $`r LS_BASIS_EQ`$, being $`r LS_BASIS`$ not necessarily orthonormal,
where a respondent is represented by vector $`r TRAIT_VEC_IN_LS`$.
According to the `r MODEL_ACRONYM` model, the probability of
a positive response to item $`r ITEM_INDEX`$ is

>>>>

Consider a basis $`r LS_BASIS_EQ`$,
with $`r LS_BASIS`$ generally non-orthonormal.
Let $`r LATENT_SPACE`$ be a $`r N_DIMS`$-dimensional latent space
in basis $`r LS_BASIS`$ (with $`r N_DIMS`$ any positive integer),
where a respondent is represented by vector $`r TRAIT_VEC_IN_LS`$.
According to the `r MODEL_ACRONYM` model, the probability of
a positive response to item $`r ITEM_INDEX`$ is
